---
title: "Asian Open Source Communities"
format: html
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(DT)
library(leaflet)

# Read communities data
communities <- read_csv("data/communities.csv")
```

# Welcome to Asian Open Source Communities

This interactive database showcases open source communities across Asia. Use the filters below to explore communities by region, category, or search for specific communities.

## Interactive Database

```{r}
#| label: datatable
#| output: html
datatable(
  communities,
  filter = 'top',
  options = list(
    pageLength = 10,
    autoWidth = TRUE
  )
)
```

## Community Map

```{r}
#| label: map
#| output: html
# Note: This is a placeholder. You'll need to add geocoding data to make this work
leaflet() %>%
  addTiles() %>%
  setView(lng = 100, lat = 20, zoom = 3)
```

## How to Contribute

We welcome new community submissions! To add your community:

1. Create a GitHub Issue using our template
2. Fill in your community details
3. Our team will review and add your community to the database

For more details, see our [Contribution Guidelines](CONTRIBUTING.md). 