---
title: "Asian Open Source Communities"
format: html
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(DT)
library(leaflet)

# Read communities data
communities <- read_csv("data/communities.csv")

# Define region coordinates
region_coords <- tribble(
  ~region, ~lat, ~lng, ~color,
  "East Asia", 35.0, 115.0, "red",
  "Southeast Asia", 10.0, 106.0, "blue",
  "South Asia", 23.0, 80.0, "green",
  "Central Asia", 45.0, 68.0, "purple"
)

# Create popup content for each region
region_data <- communities %>%
  group_by(region) %>%
  summarise(
    community_count = n(),
    community_list = paste(
      paste0("<b>", name, "</b><br>",
             description, "<br>",
             "<a href='", website, "' target='_blank'>Website</a>"),
      collapse = "<br><br>"
    )
  ) %>%
  left_join(region_coords, by = "region")
```

# Welcome to Asian Open Source Communities

This interactive database showcases open source communities across Asia. Use the filters below to explore communities by region, category, or search for specific communities.

## Interactive Database

```{r}
#| label: datatable
#| output: html
datatable(
  communities,
  filter = 'top',
  options = list(
    pageLength = 10,
    autoWidth = TRUE
  )
)
```

## Community Map

```{r}
#| label: map
#| output: html
leaflet() %>%
  addTiles() %>%
  setView(lng = 100, lat = 25, zoom = 4) %>%
  addCircleMarkers(
    data = region_data,
    lng = ~lng,
    lat = ~lat,
    color = ~color,
    radius = ~sqrt(community_count) * 10,
    fillOpacity = 0.6,
    stroke = TRUE,
    weight = 2,
    popup = ~paste0(
      "<h4>", region, "</h4>",
      "<p><b>", community_count, " communities</b></p>",
      "<div style='max-height: 200px; overflow-y: auto;'>",
      community_list,
      "</div>"
    )
  ) %>%
  addLegend(
    position = "bottomright",
    colors = region_coords$color,
    labels = region_coords$region,
    title = "Regions",
    opacity = 0.7
  )
```

## How to Contribute

We welcome new community submissions! To add your community:

1. Create a GitHub Issue using our template
2. Fill in your community details
3. Our team will review and add your community to the database

For more details, see our [Contribution Guidelines](CONTRIBUTING.md). 