---
title: "Open Source Communities in Asia"
format: html
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(DT)
library(leaflet)

# Read communities data
communities <- read_csv("data/communities.csv")

# Select display columns
display_communities <- communities %>%
  select(name, description, website, region, category)

# Define region coordinates with adjusted positions
region_coords <- tribble(
  ~region, ~lat, ~lng, ~color,
  "Eastern Asia", 35.0, 115.0, "#e74c3c",  # Red
  "South-Eastern Asia", 10.0, 106.0, "#3498db",  # Blue
  "Southern Asia", 23.0, 80.0, "#2ecc71",  # Green
  "Western Asia", 35.0, 40.0, "#9b59b6",  # Purple
  "Central Asia", 45.0, 68.0, "#f1c40f"   # Yellow
)

# Create a geocoding function (simplified for major cities)
get_coords <- function(city, country) {
  coords <- list(
    "New Delhi" = c(28.6139, 77.2090),
    "Mumbai" = c(19.0760, 72.8777),
    "Bangalore" = c(12.9716, 77.5946),
    "Tokyo" = c(35.6762, 139.6503),
    "Singapore" = c(1.3521, 103.8198),
    "Seoul" = c(37.5665, 126.9780),
    "Hong Kong" = c(22.3193, 114.1694),
    "Dubai" = c(25.2048, 55.2708),
    "Taipei" = c(25.0330, 121.5654),
    "Kolkata" = c(22.5726, 88.3639),
    "Hyderabad" = c(17.3850, 78.4867),
    "Chennai" = c(13.0827, 80.2707),
    "Pune" = c(18.5204, 73.8567),
    "Ahmedabad" = c(23.0225, 72.5714),
    "Kochi" = c(9.9312, 76.2673),
    "Lahore" = c(31.5204, 74.3587),
    "Islamabad" = c(33.6007, 73.0679),
    "Kathmandu" = c(27.7172, 85.3240),
    "Abu Dhabi" = c(24.4539, 54.3773),
    "Jakarta" = c(-6.2088, 106.8456)
  )
  
  if (!is.null(coords[[city]])) {
    return(coords[[city]])
  } else {
    # Return country-level coordinates (simplified)
    country_coords <- list(
      "India" = c(20.5937, 78.9629),
      "Japan" = c(36.2048, 138.2529),
      "Singapore" = c(1.3521, 103.8198),
      "South Korea" = c(35.9078, 127.7669),
      "China" = c(35.8617, 104.1954),
      "Taiwan" = c(23.5937, 121.0254)
    )
    return(country_coords[[country]] %||% c(NA_real_, NA_real_))
  }
}

# Add coordinates to communities data
communities_with_coords <- communities %>%
  mutate(
    coords = map2(city_state, country, ~get_coords(.x, .y)),
    lat = map_dbl(coords, ~.x[1]),
    lng = map_dbl(coords, ~.x[2])
  )

# Create region-level data for communities without specific coordinates
region_data <- communities %>%
  group_by(region) %>%
  summarise(
    community_count = n(),
    community_list = paste(
      paste0("<b>", name, "</b><br>",
             description),
      collapse = "<br><br>"
    )
  ) %>%
  left_join(region_coords, by = "region")
```

::: {.container .mt-6 .pt-6}
# {.mb-4 .border-0}

::: {.mb-5}
This interactive database showcases open source communities across Asia. Use the filters below to explore communities by region, category, or search for specific communities.
:::

## Interactive Database {.mt-5 .mb-4}

```{r}
#| label: datatable
#| output: html
datatable(
  display_communities,
  filter = 'top',
  options = list(
    pageLength = 10,
    autoWidth = FALSE,
    scrollX = FALSE,
    columnDefs = list(
      list(width = '20%', targets = 0),  # name
      list(width = '35%', targets = 1),  # description
      list(width = '15%', targets = 2),  # website
      list(width = '15%', targets = 3),  # region
      list(width = '15%', targets = 4)   # category
    )
  )
)
```

## Community Map {.mt-5 .mb-4}

```{r}
#| label: map
#| output: html
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  setView(lng = 100, lat = 25, zoom = 4) %>%
  # Add region markers
  addCircleMarkers(
    data = region_data,
    lng = ~lng,
    lat = ~lat,
    color = ~color,
    radius = ~sqrt(community_count) * 8,
    fillOpacity = 0.4,
    stroke = TRUE,
    weight = 2,
    group = "Regions",
    popup = ~paste0(
      "<h4>", region, "</h4>",
      "<p><b>", community_count, " communities</b></p>",
      "<div style='max-height: 200px; overflow-y: auto;'>",
      community_list,
      "</div>"
    )
  ) %>%
  # Add specific location markers
  addCircleMarkers(
    data = communities_with_coords %>% filter(!is.na(lat)),
    lng = ~lng,
    lat = ~lat,
    radius = 6,
    color = "#2c3e50",
    fillOpacity = 0.8,
    stroke = TRUE,
    weight = 1,
    group = "Communities",
    popup = ~paste0(
      "<h4>", name, "</h4>",
      "<p>", description, "</p>"
    )
  ) %>%
  addLegend(
    position = "bottomright",
    colors = region_coords$color,
    labels = region_coords$region,
    title = "Regions",
    opacity = 0.7
  ) %>%
  addLayersControl(
    overlayGroups = c("Regions", "Communities"),
    options = layersControlOptions(collapsed = FALSE)
  )
```

## How to Contribute {.mt-5 .mb-4}

We welcome new community submissions! To add your community:

1. Create a GitHub Issue using our template
2. Fill in your community details
3. Our team will review and add your community to the database

For more details, see our [Contribution Guidelines](CONTRIBUTING.md).
:::
