---
title: "Communities"
format: html
---

# Asian Open Source Communities

Browse through our comprehensive list of open source communities across Asia. Use the filters below to find communities by region or category.

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(DT)

# Read communities data
communities <- read_csv("../data/communities.csv")

# Select only the columns we want to display
display_communities <- communities %>%
  select(name, description, website, region, category)
```

## Community Directory

```{r}
#| label: datatable
#| output: html
datatable(
  display_communities,
  filter = 'top',
  options = list(
    pageLength = 10,
    autoWidth = FALSE,
    scrollX = FALSE,
    columnDefs = list(
      list(width = '20%', targets = 0),  # name
      list(width = '35%', targets = 1),  # description
      list(width = '15%', targets = 2),  # website
      list(width = '15%', targets = 3),  # region
      list(width = '15%', targets = 4)   # category
    )
  )
)
```

## How to Add Your Community

If your community is not listed, you can add it by:
1. Creating a GitHub Issue using our template
2. Submitting a Pull Request with your community details

See our [Contribution Guidelines](../contribute.html) for more information. 